### 2020-12-02 05_Thesis/THESIS_LaTeX/Chapters/5.tex
able to fit lin
final work done

\chapter{Comparison of the Obtained Carbon Fibres Against SU8-based Carbon Fibres and Potential Applications} % Main chapter title

@@

%----------------------------------------------------------------------------------------
%	SECTION 1
%----------------------------------------------------------------------------------------
\section{Characterization \& Reproducibility}

%Were the selected candidates electrospunable?
%Fiber morphology

>>>>

\chapter{Concluding Remarks} % Main chapter title

@@

%----------------------------------------------------------------------------------------
%	SECTION 1
%----------------------------------------------------------------------------------------
\section{Conclusions}

As stated within the introductory chapter \ref{Chapter:1}, this thesis is to verify the near-field electrospinnability of high-carbon oxygen-less polymers in solution. The spinnability of the tested solutions is used as a screening to choose candidate formulations that can replace the PEO in SU-8 solution. A near-field electrospinning literature review was used to learn about the effect of the process parameters and solution properties in the control of the fiber diameter. The review analyses (data analysis, parameter correlation, and adimensional analysis) declare that the polymer concentration is the parameter with the biggest impact on the fiber diameter, followed by the applied voltage, the working distance, and the zero-shear viscosity.

Rheological analyses were performed to determine the viscoelastic properties of the candidate polymer solutions. Zero-shear viscosities of the solutions in interest are measured  to find solutions with spunable polymer concentrations. As explained in the following, viscosity and polymer concentration have a significant impact on the spinnablity of polymer solutions, but they are not sufficient by themselves. As demonstrated by the experiments to fabricate fibers through NFES, PSMS in DMF and PSB in NMP formulations were not spinnable at their critical concentrations.

A series of experiments were carried out in order to find a correlation between the rheological properties of different polymer solutions in near-field electro-mechanical spinning for carbon structures. Flow curve measurement tests where carried out in an oscillatory rheometer to estimate the critical concentrations of various polymer-solvent systems at which they are spinnable by NFES. Since the formulation is 0.25 $wt\%$ PEO in SU-8 2002 has been studied in the past and is known to yield good polymer solutions but fails at the pyrolysis, this work intends to find spinnable and pyrolyzable systems as well as a method to discover new spinnable polymer solutions.

From the flow curve measurements, the zero-shear viscosity was estimated using the Carreau-Yassuda model. For all solutions, a shear thinning behavious was noticed. It was found that the viscosity-concentration plot is a good method to find the critical concentration at which the solution is able to produce fibers through NFES. However the method failed at calculating the spinnable concentration of PSMS. An significant takeaway is that a polymer does not have elastic properties in the pellet form, it will probably not work as a NFES polymer precursor.

Fibers were fabricated at different applied voltages for each set of solutions in order to very that in NFES fiber diameter increases with increasing applied voltage, whereas the inverse relationship is true for FFES. Other parameters such as working distance, stage velocity, nozzle diameter, flow rate were kept constant for all experiments; however, for low applied voltages the jet shall be initialed by manually breaking the polymer drop. the thickest average fiber diameter was achieved with the PS in THF system ($\Phi_0 = 600 V$, $D_{fiber} = 5.304 \mu m$) and the thinnest was $0.976 \mu m$ using the PVK in CHL system and an applied voltage of $200 V$. It was proved that attainable rehological information can be used to modify the NFES process parameters to yield the desired fiber morphology.

Moreover a data analysis was done on the NFES publications of the last 13 years to identify relationships between fiber diameter and the process parameters. For instance, it was confirmed that thin fibers are achived with los polymer concentrations, small nozzle diameters, low applied voltage, slow flow rates and high stage velocities. Also, using the collected data and the input of Helgeson's work \cite{Helgeson2007}, an dimensionless analysis was done to predict fiber diameters with easy to get parameters.

Finally, the fabricated fibers can be classified into three groups: a) the control sample (PEO in SU-8); b) poor quality fibers (PS in THF, and PSB in THF and DMF); and c) good quality fibers (PVK in CHL and PVK in SU-8). PS and PSB fibers have rough textures and low adhesion to the collector substrate. The rough surface and low adhesion is due to the rapid solvent volatilization, which results in fibers to solidify before landing on the substrate. The fast solidification minimize the fiber adhesion to the collector, causing the fibers to slip, and therefore the mechanical drag force in the fibers is reduced. Due to the low influence of the mechanical force, fibers are not stretched by the moving stage, which may explain the rough surface.

On the other hand, the formulation regarding PVK deposited smooth fibers with good adhesion to the substrate, similar to the PEO/SU-8 solution. The thinnest fibers ($700 \textrm{ nm}$ in diameter) were achieved PVK in CHL formulation. Moreover, the PVK in SU-8 solution seems to be the formulation to replace the PEO in SU-8 solution. Assuming that the additional oxygen content in PEO negatively affects the fiber yield rate and electrical resistivity variance due to degassing during pyrolysis, the PCK does not contain additional oxygen content and has sp2-hybridized carbon which can promote the formation of graphitic carbon during pyrolysis. The already oxygen in SU-8 is necesary to create closed pores during annealing, characteristic of glass-like carbon.

\section{Future work}

Apart from the work done, this dissertation opens pending research to enable NFES for the fabrication of carbon structures. The following lists future work that could be done as a continuation of this thesis.

\begin{itemize}
\item Helgeson's model \cite{Helgeson2007} was thought to work with far-field electrospinning, hence the deviation of the NFES data from the model trend. For an accurate NFES fiber diameter prediction, the mechanical stresses introduced by the moving stage shall be considered in the model (Equation \ref{eqn:ohnesorgeNumberRelationship}). 
\item This work verifies the electro-spinnability of four new formulations, however fibers were not carbonized into carbon structures. Further work shall study the pyrolysis process of the proposed fibers to get carbon structures with good electrical conductivity. A photo-polymerization process could be introduced before pyrolyzation to increase the order of the molecules and achieve carbon with higher conductivity.
\item Near-field electrospinning solutions require specific viscosities to initialte a polymer jet. The viscosity-concentration plot is a helpful tool to estimate the critical spinnable concentration of a polymer-solvent system. However there is room for improvement as this method only considers reological data. Other methods could be adopted to better tune other process parameters such as stage velocity, and applied voltage.
\end{itemize}

% enhance conductivity with photopolymerization, CNT streching, ...

### 2020-12-02 05_Thesis/THESIS_LaTeX/main.tex
defense update
slides update
final work done

@@

@@

% Your thesis title, this is used in the title and abstract, print it elsewhere with \ttitle
\thesistitle{Fabrication of Suspended Nanowires Through Mechano-Near-Field Electrospinning of Polymers in Solution for the Production of Glass-like Carbon}

@@

\noindent \rule[0.0em]{15em}{0.5pt}\\ % This prints a line for the signature
%\href{http://www.alanaguirre.com}{\supname}
\cosupname\\
Tecnológico de Monterrey\\
\emph{Co-Advisor}

@@

\noindent \rule[0.0em]{15em}{0.5pt}\\ % This prints a line for the signature
%\href{http://www.alanaguirre.com}{\supname}
Dr. Marc Madou\\
University of California\\
\emph{Committee Member}

@@

\noindent \rule[0.0em]{15em}{0.5pt}\\ % This prints a line for the signature
%\href{http://www.alanaguirre.com}{\supname}
Dr. Sergio Omar Martínez Chapa\\
Tecnológico de Monterrey\\
\emph{Committee Member}

@@

\noindent \rule[0.0em]{15em}{0.5pt}\\ % This prints a line for the signature
Dr. Martín Rogelio Bustamante Bello \\
\emph{Associate Dean of Graduate Students}\\
\deptname\\
%\href{http://www.doramedina.com}{\supname}

@@

Carbon nano-wires are versatile materials composed of carbon chains with a wide range of applications due to their high conductivity. Regardless of the high interest in the implementation of carbon nano-wires in several applications and devices, no feasible processes have been developed to fabricate carbon nano-wires with spatial control at a reasonable cost. Carbon nano-wires have been fabricated with the use of a photoresist, but little is known about polymers that can produce more conductive carbon nano-wires after pyrolysis. Various polymer solutions have been tested in near field electrospinning (NFES) and photopolymerization separately, however, few have been tested for nano-wire fabrication purposes through pyrolysis. The intention behind the thesis proposal is to implement rheology analyses of different polymer solutions to determine if they can be easily electrospun at low voltages and then fabricate nano-wires with them. This thesis work arises from the need to test a greater variety of polymers with the goal to design a polymer solution to fabricate carbon nano-wires with better conductivity than the current SU-8 polymeric nano-fibers. The research process will include the design of polymer solutions that can be electrospun, photopolymerized, and then pyrolyzed into conducting carbon nanowires. On the other hand, it is intended to engineer a newly designed polymer solution to achieve mass scale manufacturing of conductive carbon nano-wires in an inexpensive, continuous, simple and reproducible manner as central components for nano-sensors. \\

@@

\include{./Chapters/1}
\include{./Chapters/2}
\include{./Chapters/3}
\include{./Chapters/4}
%\include{./Chapters/5}

@@

\include{Appendices/Appendix_ViscosityCurves}
\include{Appendices/Appendix_CriticalConcentrations}
\include{Appendices/Appendix_MicroscopyChar}

@@

\addcontentsline{toc}{chapter}{Bibliography}
\printbibliography[title={Bibliography}]

@@

\newpage 
\addcontentsline{toc}{chapter}{Curriculum Vitae}
\includepdf[page=-,fitpaper=false,landscape=false]{./pdf/CV/CV}

>>>>

\usepackage{xltabular}
\usepackage{longtable}

@@

% import code snippets
\usepackage{listings}
\usepackage{xcolor}
\definecolor{codegreen}{rgb}{0,0.6,0}
\definecolor{codegray}{rgb}{0.5,0.5,0.5}
\definecolor{codepurple}{rgb}{0.58,0,0.82}
\definecolor{backcolour}{rgb}{0.99,0.99,0.96}
\lstdefinestyle{mystyle}{
  backgroundcolor   = \color{backcolour},
  commentstyle      = \color{codegreen},
  keywordstyle      = \color{magenta},
  numberstyle       = \tiny\color{codegray},
  stringstyle       = \color{codepurple},
  basicstyle        = \ttfamily\small,
  breakatwhitespace = false,
  breaklines        = true,
  captionpos        = b,
  keepspaces        = true,
  numbers           = left,
  numbersep         = 2pt,
  showspaces        = false,
  showstringspaces  = false,
  showtabs          = false,
  tabsize           = 2,
  aboveskip         = 0.1em,
  belowskip         = 0.1em
}
\lstset{style=mystyle}

@@

% Your thesis title, this is used in the title and abstract, print it elsewhere with \ttitle
\thesistitle{Search for high-molecular weight linear polymers for the formulation of novel solutions for the fabrication of micro fibers by electromechanical spinning}
% Fabrication of Suspended Nanowires Through Mechano-Near-Field Electrospinning of Polymers in Solution for the Production of Glass-like Carbon

@@

\noindent \rule[0.0em]{15em}{0.5pt}\\ % This prints a line for the signature
%\href{http://www.alanaguirre.com}{\supname}
\cosupname\\
Tecnológico de Monterrey\\
\emph{Co-Advisor and Director of Program}

@@

\noindent \rule[0.0em]{15em}{0.5pt}\\ % This prints a line for the signature
%\href{http://www.alanaguirre.com}{\supname}
Dr. Marc Madou\\
University of California, Irvine\\
\emph{Committee Member}

@@

\noindent \rule[0.0em]{15em}{0.5pt}\\ % This prints a line for the signature
%\href{http://www.alanaguirre.com}{\supname}
Dr. Jaime Bonilla Ríos\\
Tecnológico de Monterrey\\
\emph{Committee Member}

@@

\noindent \rule[0.0em]{15em}{0.5pt}\\ % This prints a line for the signature
Dr. Rubén Morales Menéndez \\
\emph{Associate Dean of Graduate Students}\\
\deptname\\
%\href{http://www.doramedina.com}{\supname}

@@

Carbon nano-wires are versatile structures composed of carbon chains with a wide range of applications due to their high chemical resistance and electric properties. Regardless of the high interest in the implementation of carbon nano-wires in energy, environmental and health-care applications, no feasible processes have been developed to fabricate carbon nano-wires with spatial control at a reasonable cost. Carbon nano-wires have been fabricated with the use of a photoresist, but little is known about polymers that can produce conductive carbon nano-wires after pyrolysis. Various polymer solutions have been tested in near field electrospinning (NFES) and photopolymerization separately, however, few have been tested for nano-wire fabrication purposes through the process of spatio-temporal deposition with NFES, photo-polymerization for cross-linking and pyrolysis. The intention behind the thesis proposal is to use rheological analyses of different polymer solutions to determine if they can be easily electrospun at low voltages and then fabricate nano-wires with them. This thesis work arises from the need to test a greater variety of polymer-solvent combinations with the goal of designing a polymer solution to fabricate carbon nano-wires with higher conductivity than the current SU-8 polymeric nano-fibers. The present work includes the design of polymer solutions that can be electrospun, with the hope that the selected high molecular weight polymers can be photo-polymerized, and then pyrolyzed into conducting carbon nanowires. The overarching goal is to contribute towards the development of novel designed polymer solutions to achieve mass scale manufacturing of conductive carbon nano-wires in an inexpensive, continuous, simple and reproducible manner as central components for nano-sensors. \\

@@

\include{./Chapters/1}
\include{./Chapters/2}
\include{./Chapters/3}
\include{./Chapters/4}
\include{./Chapters/5}

@@

\include{Appendices/Appendix_ViscosityCurves}
\include{Appendices/Appendix_CriticalConcentrations}
\include{Appendices/Appendix_MicroscopyChar}
\include{Appendices/Appendix_FiberDiameters}
\include{Appendices/Appendix_ReviewTable}
\include{Appendices/Appendix_ImageAnalysisCode}

@@

\printbibliography[heading=bibintoc, title={Bibliography}]
% \addcontentsline{toc}{chapter}{Bibliography}

@@

% \includepdf[page=-,fitpaper=false,landscape=false]{./pdf/CV/CV}
